The connection between star formation rate and dark matter halo mass in the epoch of reionization

### 2015-04-21 paper/ms.tex

\keywords{galaxies: high-redshift --- methods: numerical} 
\begin{abstract}
We procent updated constraints between the star formation rate and
dark matter halo mass at redshift $z\sim 6$.
The observational basis for our work is the luminosity function data
obtained with  from CFHTLS, HST Legacy Survey and UKIDSS.
The constrains are based on an abundance matching method using data
from cosmological N-body simulations in order to take into account the impact
of cosmic variance in our estimates.

\end{abstract}

>>>>

\keywords{galaxies: high-redshift --- methods: numerical} 
\begin{abstract}
We present updated constraints between the star formation rate and
dark matter halo mass at redshift $z\sim 6$.
The observational basis for our work is the luminosity function data
obtained with from CFHTLS, HST Legacy Survey and UKIDSS.
The constrains are based on an abundance matching methodology using data
from cosmological N-body simulations in order to take into account the impact
of cosmic variance in our estimates.
\end{abstract}
